Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-11-19 ms.tex
Fixing order of variable definitions and adding oscillator strength of lya from rybicki and lightman

Consider a sphere of radius $R$ with uniform density $n_{\rm sc}$, luminosity $L$, and line-center optical depth $\tau_0$ containing a point source of photons. We aim to find the intensity within the sphere as a function of radius and photon frequency. The point source is assumed to be a delta function in space and photon frequency. Photons of frequency $\nu$ near the line center frequency $\nu_0$ are considered. The photon frequency of the source is $\nu_s$. The Doppler width is $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light. The photon frequency in Doppler widths is $x = (\nu-\nu_0)/\Delta$, and $x_s = (\nu_s - \nu_0)/\Delta$ is the corresponding source frequency. For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$. For the \lya transition and T=$10^4$ K, $a = 4.72\times 10^{-4}$. $\mathcal{H}(x,a)$ is the Voigt function, $k = n_{\rm sc} \pi e^2 f/(m_e c)$, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$. The line center optical depth is then $\tau_0 = kR/(\sqrt{\pi}\Delta)$. 
% Here $e$ and $m_e$ are the charge and mass of the electron, $f$ is the oscillator strength of the transition, 
% Add the oscillator strength (number) cite Rybicki and Lightman

>>>>

Consider a sphere of radius $R$ with uniform density $n_{\rm sc}$, luminosity $L$, and line-center optical depth $\tau_0$ containing a point source of photons. We aim to find the intensity within the sphere as a function of radius and photon frequency. The point source is assumed to be a delta function in space and photon frequency. Photons of frequency $\nu$ near the line center frequency $\nu_0$ are considered. The photon frequency of the source is $\nu_s$. The Doppler width is $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light. The photon frequency in Doppler widths is $x = (\nu-\nu_0)/\Delta$, and $x_s = (\nu_s - \nu_0)/\Delta$ is the corresponding source frequency. For upper-state de-excitation rate $\Gamma$, the ratio of natural to Doppler broadening is $a=\Gamma/(4\pi \Delta)$. For the \lya transition and T=$10^4$ K, $a = 4.72\times 10^{-4}$. $\mathcal{H}(x,a)$ is the Voigt function, and the Voigt line profile is $\phi = \mathcal{H}(x,a)/(\sqrt{\pi} \Delta)$, which is normalized as $\int d\nu\, \phi(\nu) = 1$. The line center optical depth is $\tau_0 = kR/(\sqrt{\pi}\Delta)$, where $k = n_{\rm sc} \pi e^2 f/(m_e c)$. Here, $e$ and $m_e$ are the charge and mass of the electron, and $f$ is the oscillator strength of the transition, which is 0.4162 for \lya \citep{1986rpa..book.....R}.
